Total Platform Cyber Protection

### 2016-06-25 paper.tex
adding todos, and adding a pre-commit-hook
mitigation & recovery part updated

% Sai: should this be 'arranged' instead of 'arraigned'?%Faris: I think it should be 'arranged'.
The layers are arraigned from lowest to highest layer. The lower layer
has more control over the computing system, while the upper layers
have less control. For instance, the Hardware layer has total control
over the physical hardware and memory of the machine, while an
application running in the Application layer can only see a portion of
the machine's memory (because of the virtual memory used by the
Operating System).

@@

The malicious Trojan logic behavior comes in three different forms:
% Sai: is this three or two??

@@

>>>>

The layers are arranged from lowest to highest layer. The lower layer
has more control over the computing system, while the upper layers
have less control. For instance, the Hardware layer has total control
over the physical hardware and memory of the machine, while an
application running in the Application layer can only see a portion of
the machine's memory (because of the virtual memory used by the
Operating System).

@@

The malicious Trojan logic behavior comes in three different forms:
% TODO: Sai: is this three or two??

@@

Mitigation and recovery is of major concern when it comes to application and systems security. This area of research is important because recovery of a tainted system is the first concern post attack or exploitation.

Researchers have found some VM-based approaches in order to recover from intrusions.~\cite{zhang2009b} suggest one such approach. They try to achieve recovery in three phases, Routine execution phase, Damage assessment phase and Recovery phase. This framework tries to log pre-attack states and system calls and takes forward or reverse taint-tracking approach. Recovery phase tries to Quarantine the malicious files and objects identified during the Damage assessment.

A similar VM-based approach is taken in~\cite{oliveria2008b}. The Bezoar framework proposed in this paper tries to recover a system based on monitoring of propagation bytes in the system after hijacking attack has been detected. The framework replays the checkpointed run while ignoring inputs from malicious sources.

Automated intrusion recovery system is proposed in~\cite{goel2005b}. Researchers have designed automated resolution policies which determines set of tainted files. Taser recovery system~\cite{goel2005b}, is designed based on following models. Recovery model, Audito, Analyzer and Resolver. Techniques like naming conventions and file permissions, logging of all events, dependency of files, process and sockets are used by Taser in order to analyze intrusion. Similar to Recovery phase approach taken in~\cite{zhang2009b}, Taser uses the Resolver model proposed to go back to the state of the operating system before intrusion.

The research in this area of mitigation and recovery is majorly done taking the VM-based approach in consideration.
